---
title: "Check-in 2"
author: "Amelia Le"
date: "2023-08-28"
output: html_document
---

You should edit this .Rmd using RStudio, then click *Render* in the menu bar of the Source window (above the text of this .Rmd). Remember, you must submit *both* your .Rmd and the compiled .html in order to receive full credit!

### Collaborators

INSERT NAMES OF ANY COLLABORATORS

## A. Functions

Work with one or two other students,

**1.** In words, what does the following line of code do?

```{r, eval = T}
sample(1:6, 1)
```

The line of code is randomly generation a value from 1 to 6 and returning that value. 

**2.** Run the line of code in RStudio. What do you get? What did your groupmates get? What happens to the result each time you knit the document?

The code returns the value 3 when it first ran, and the result changes each time the document is knitted.

**3.** Below, we introduce the `set.seed` function. What do the two lines of code below do? What does the `456` mean? What happens to the result each time you knit the document?

```{r, eval = T}
set.seed(456)
sample(1:6, 1)
```

The set.seed() function allows for the random number generator code to return a reproducible result each time we run it. The `456` is use as a starting point for the set.seed() function. 


## B. Vectors and Matrices

**4.** Write a line of code to generate a vector of length 100 whose entries are 1, 2, ..., 100.

```{r, eval = T}
x <- c(1:100)
x
```

**5.** Write a line of code to generate the following matrix:

`1 2 3`

`4 5 6`

`7 8 9`


```{r, eval = T}

my_matrix <- matrix(c(1:9), nrow = 3, ncol = 3, byrow = T)
my_matrix
```