---
title: "Check-in 3"
author: "Amelia Le"
date: "2023-09-11"
format: 
  html:
    embed-resources: true
    code-tools: true
    code-summary: "Code"
---

Remember, you must submit *both* your .Rmd and the compiled .html in order to receive full credit! In addition, to receive full credit, your code output and plots must be correctly formatted.

### Collaborators

INSERT NAMES OF ANY COLLABORATORS

## A. Weather Forecast Data

**1.**  For this lab, we'll be using the `flights` data. You can load this data using the following code:

```{r}
library(nycflights13)
data(flights)
library(tidyverse)
```

**2.** Use the `mutate()` function to turn `origin` into a factor.

```{r}
flights <- flights |> 
  mutate(origin = as.factor(origin))
```

**3.** Compute the mean `arr_delay` for each origin airport. Which airport has the longest delays on average? You can drop missing rows.

```{r}
# Group by the airports then when finding the mean arrive delay time drop all the missing rows.
flights |> 
  group_by(origin) |>
  summarize(mean_arr_delay = mean(arr_delay, na.rm = T)) |>
  ungroup()
```

EWR has the longest delay on average with an average of 9.1 minutes. 


**4.** Use the `mutate()` function to turn `month` into a factor.

```{r}
flights <- flights |> 
  mutate(month = as.factor(month))
```


**5.** Compute the mean `arr_delay` by month. What do you notice?

```{r}
flights |> 
  group_by(month) |>
  summarize(mean_arr_delay = mean(arr_delay, na.rm = T)) |>
  ungroup()
```
The month that has the longest average arrival delay time is June with an average of 16.7 minutes delay, and the month with the shortest arrival delay time is September with an average of arriving 4 minutes earlier than predicted. 



**6.** Compute the mean `arr_delay` by month AND airport. What do you notice?

```{r}
flights |> 
  group_by(month, origin) |>
  summarize(mean_arr_delay = mean(arr_delay, na.rm = T)) |>
  ungroup()
```
The EWR airport consistently has the longest arrival delay time for the majority of the months which is consistent with the finding from part 3 above. However, there were some months that the JFK airport has longest arrival delay time but the time difference between the airports for those months were not as drastic as the months where EWR has the longest arrival delay time.

