---
title: "Check-in 8"
author: "Amelia Le"
date: "2023-10-30"
format: 
  html:
    embed-resources: true
    code-tools: true
    code-summary: "Code"
---

Remember, you must submit *both* your .Rmd and the compiled .html in order to receive full credit! In addition, to receive full credit, your code output and plots must be correctly formatted.

### Collaborators

INSERT NAMES OF ANY COLLABORATORS

1. Write a function `sum_for_loop()`, that takes as input two vectors of length $n$, `x` and `y`, and returns the vector sum of `x` and `y` using a for loop of $n$ steps where the $i$th step involves adding `x[i]` and `y[i]`, Write a function `sum_vectorized()` that takes as input two vectors of length $n$, `x` and `y`, and computes the vector sum using the vectorized operator `x+y`.

```{r}
sum_for_loop <- function(x, y) {
  n <- length(x)
  z <- numeric(n)
  for (i in 1:n) {
    z[i] <- x[i] + y[i]
  }
  return(z)
}

sum_vectorized <- function(x,y) {
  return(x + y)
}
```

2. Compare the speed of your two functions using one of the approaches discussed in class today.

```{r}
set.seed(123)
x <- sample(1:10, 10)
y <- sample(1:10, 10)

start_time <- Sys.time()
sum_for_loop(x,y)
print(Sys.time() - start_time)
```

```{r}
start_time <- Sys.time()
sum_vectorized(x,y)
print(Sys.time() - start_time)
```

The sum_vectorized function that compute the vectors sum using the vectorize operator `+` is almost 10 times faster than the sum_for_loop that uses the for loop to add each entry of both vectors together.
