---
title: "Lab 1: Basic Definitions"
author: "Amelia Le"
date: "2023-08-23"
output: html_document
---

## A. Combining R code and output

1.  **Explain what the following code does in your own words.**

    ```{r}
    x <- 1
    y <- 1
    print(x + y)
    ```

We assigned the value 1 to both the 'x' and 'y' variables. Then we print out the result of the operation 'x + y'.

## B. Running an R script

1.  **Download the `01_lab-test-code.R` file and put it in the same folder as this lab. Change the chunk option `eval = F` to `eval = T`. What does this code file do?**

    ```{r, eval = T}
    source("01_lab-test-code.R")
    ```

The file print out "NICE ONE: You put the R file in the right place."

## C. Exercises

1.  **In contrast to the usual mathematical interpretation of x = x + 1, which has no finite solution, the following assignment evaluates to a finite value. Explain.**

    ```{r}
    x <- 1
    x <- x + 1
    print(x)
    ```

 Since we only update the x variable once rather than in an inifinite loop, the following assignment evaluates to a finite value which is 2. 

2.  **The first expression below evaluates to a numeric value, but the second one causes an error. Explain.**

    ```{r, error = T}
    T + 1
    T + "Hello"
    ```

  The second expression causes an error because we cannot perform an arithmetic operation on a string variable.

3.  **Correct the code below so `example_chr` is an object of the character class.**

    ```{r}
    # YOUR CODE HERE
    example_chr <- "T"
    class(example_chr)
    ```

4.  What questions do you have about R, RStudio, and RMarkdown?

    1.  What are the differences between RMarkdown and RStudio? 

    2. Is R better than Python in term of accurately doing mathematical computation works?

```{r}

```
