---
title: "Lab 9"
author: "Amelia Le"
date: "2023-11-15"
format: 
  html:
    embed-resources: true
    code-tools: true
    code-summary: "Code"
---

Remember, you must submit *both* your .Rmd and the compiled .html in order to receive full credit! In addition, to receive full credit, your code output and plots must be correctly formatted.

### Collaborators

```{r, warning=FALSE, message=FALSE}
library(palmerpenguins)
library(tidyverse)
library(dbplyr)
```


## A. Bootstrapping the sampling distribution of the median

1. Using the `penguins` dataset in the `palmerpenguins` package, construct a confidence interval for the mean `body_mass_g` for female Adelie penguins based on using a normal distribution based on the central limit theorem. You should compute the confidence interval without using `confint()`.

```{r}
attach(penguins)

df_adelie <- penguins |> 
  subset(species == "Adelie" & sex == "female")

n <- length(df_adelie$species)
mu <- mean(df_adelie$body_mass_g, na.rm=TRUE)
sigma <- sd(df_adelie$body_mass_g, na.rm=TRUE)

upper = mean(rnorm(n, mean = mu, sd = sigma)) + 1.96 * sigma / sqrt(n)
lower = mean(rnorm(n, mean = mu, sd = sigma)) - 1.96 * sigma / sqrt(n)
```

The 95% confident interval for the mean body mass for female Adelie penguins is between `r lower` grams and `r upper` grams.

2. Construct a bootstrap confidence interval for the mean `body_mass_g` for female Adelie penguins using 10000 resamples.

```{r}
Xbars <- replicate(1000, mean(sample(df_adelie$body_mass_g, size = 10000, replace = TRUE)))
quantile(Xbars, probs = c(.025, .975))
```

3. Construct a bootstrap confidence interval for the median `body_mass_g` for female Adelie penguins using 10000 resamples.

```{r}

Xtilde <- replicate(1000, median(sample(df_adelie$body_mass_g, size = 10000, replace = TRUE)))
quantile(Xtilde, probs = c(.025, .975))

```

## B. Simulations

4. Suppose that $Y\sim \mathrm{Poisson}(X)$ where $X\sim \mathrm{Exponential}(1)$. Use simulation to estimate $E(Y)$ and $\mathrm{Var}(Y)$.

```{r}
Y <- replicate(10000, rpois(100,rexp(100, rate = 1)))
Ybar <- mean(Y)
Yvar <- sd(Y)^2
```

The estimated $E(Y)$ is `r Ybar` and the estimated $\mathrm{Var}(Y)$ is `r Yvar`

5. For this question, you will write a simulation to test the frequentist coverage of a 95\% confidence interval for a proportion based on the normal approximation. 

    a. First, write a function that takes two inputs: `n` and `p`. Your function should randomly generate some $X\sim \mathrm{Binomial}(n, p)$, compute $\widehat{p}= X/n$, and then compute the corresponding normal distribution-based confidence interval for $p$ **based on your sample** $\widehat{p}$. Your function should return `TRUE` if $p$ is in the confidence interval. You may use the following formula for the confidence interval:
    
    $$\widehat{p}\pm z_{.975}\sqrt{\frac{\widehat{p}(1-\widehat{p})}{n}}$$
        
```{r}
binom <- function(n,p) {
  X <- sum(rbinom(n, size = 1, p))
  phat = X/n
  upper = phat + 1.96 * sqrt((phat * (1-phat))/(n))
  lower = phat - 1.96 * sqrt((phat * (1-phat))/(n))
  if (p > lower & p < upper) {
    return(TRUE)
  } else {
    return(FALSE)
  }
}
```
        
    b. Next, write a second function that takes three inputs: `n`, `p`, and `n_runs`, representing the number of times to run your simulation. This function should use your function from (a) to simulate `n_runs` binomial random variables and return the proportion of the `n_runs` for which $p$ is contained in the confidence interval.
    
```{r}
binom_runs <- function(n, p, nruns) {
  x <- replicate(nruns, binom(n,p))
  p <- sum(x * 1) / nruns
  return(p)
}
```

    c. Test your function from (b) with `n = 20`, `p = .5`, and `n_runs = 1000`.
    
```{r}
binom_runs(20, 0.5, 1000)
```
    
    d. Use your simulation code to investigate the following questions: For what values of `n` and `p` is the frequentist coverage close to the expected 95\% value? For what values of `n` and `p` is the frequentist coverage very different to the expected 95\% value?

```{r}
x1 <- binom_runs(20, 0.5, 1000)
x2 <- binom_runs(20, 0.15, 1000)
x3 <- binom_runs(4, 0.5, 1000)
x4 <- binom_runs(4, 0.15, 1000)
```
If we keep n the same and reduce p from 0.5 to 0.15 we will see about a 0.13 drop in the expected 95% value from about 0.94 to 0.81. In Contrast, if we keep p the same and reduce the n value from 20 to 4 that is when we see a significant difference in the expected 95% value. If we change n to 4 and p to 0.15 then we will see that the expected 95% value reduces to less than half of the initial value of around 0.96.
